


## Percentage of students completing the survey and non-respondents

```{r }
t <- df %>%
  filter(week == current_week) %>%
  summarize(total_responses = sum(responded_survey, na.rm = TRUE)) %>% pull(total_responses)
eval_condition = t/total_students < 1
```

The total number of students responding to the survey this week is: `r t`, which is equivalent to `r round(t/total_students*100, 2)`%. For those students who reported **family engagement** activities, the table below shows what each of them did.


```{r }
tbl <- df %>% filter(responded_survey == 1, week == current_week) %>%
  select(`Last Name`, `First Name`, `Family Engagement`) %>%
  arrange(`Last Name`)
knitr::kable(tbl, caption = "Specific family engagement activities reported")

```

The following table shows the name and email of students that have not responded to the survey. The table is omitted if all students have provided the expected data.


```{r eval = eval_condition}
tbl <- df %>% filter(responded_survey == 0, week == current_week) %>%
  select(`Last Name`, `First Name`, email)
knitr::kable(tbl, caption = "Name and email of non-responding students")

```

\newpage
## Students Week `r current_week` activity

The following table shows, for each student who completed the survey, the number of hours the student engaged in observation, participation and teaching. Students are listed in alphabetical order by last name.

```{r}
tbl <- df %>% filter(responded_survey == 1, week == current_week) %>%
  select(`Last Name`, `First Name`, Observations, Participation, Teaching) %>%
  arrange(`Last Name`)
knitr::kable(tbl, caption = "Students activity during the week")
```

If there are any students who reported zero engagement in all recorded activities during **Week `r current_week` ** they are listed here in alphabetical order by last name. Otherwise, no table is produced.

```{r}
tbl <- df %>% filter(responded_survey == 1, week == current_week) %>%
    filter(total_hours == 0) %>%
  select(`Last Name`, `First Name`, Observations, Participation, Teaching) %>%
  arrange(`Last Name`)
eval_condition = nrow(tbl)
```

```{r eval = eval_condition}
knitr::kable(tbl, caption = "Students reporting no activity during the week")
```

\newpage
## Cumulative students activity up to and including **Week `r current_week`**

This section provides an analysis of students activity for the duration of the semester, up to and including **Week `r current_week`**. We will present both a cumulative and per-week average analysis.

The following table reports cumulative activity in number of total for observation, participation and teaching. Students are listed in alphabetical order by last name.

```{r }
tbl <- df %>% filter(week <= current_week) %>%
  group_by(`Last Name`, `First Name`) %>%
  summarize(`Observation Total` = sum(Observations, na.rm = TRUE),
            `Participation Total` = sum(Participation, na.rm = TRUE),
            `Teaching Total` = sum(Teaching, na.rm = TRUE))
knitr::kable(tbl, caption = "Total activity for each student")
```

The following table reports average activity in number of total for observation, participation and teaching. Students are listed in alphabetical order by last name. The average is computed between **Week 1** and the current week, **Week `r current_week`**.

```{r }
tbl <- df %>% filter(week >= 1, week <= current_week) %>%
  group_by(`Last Name`, `First Name`) %>%
  summarize(`Observation Weekly` = round(mean(Observations, na.rm = TRUE), 2),
            `Participation Weekly` = round(mean(Participation, na.rm = TRUE), 2),
            `Teaching Weekly` = round(mean(Teaching, na.rm = TRUE), 2))
knitr::kable(tbl, caption = "Average weekly activity for each student")
```

\newpage
## Progress monitor for students activity up to and including **Week `r current_week`**

This section provides a visual aid to monitor students' progress toward the teaching hours target for the program. The table displays, for each student, the program, target teaching hours and the percentage of teaching hours completed to date.

```{r }
# Calculate the percentage
# The create the bar chart
tbl <- df %>%
  group_by(`Last Name`, `First Name`, Program, `Required Hours`) %>%
  summarize(`Teaching Total` = sum(Teaching, na.rm = TRUE)) %>%
              mutate(`Percentage Completion` = round((`Teaching Total` / `Required Hours`) * 100, 2))
knitr::kable(tbl, caption = "Percentage of teaching hours completed")
```

The following bar chart graphically displays the percentage completion of the LSU School of Education program requirement by each student.

```{r }
tbl %>%
  mutate(`Percentage Completion` = ifelse(`Percentage Completion` > 0,
                                          pmin(`Percentage Completion`, 100), 0)) %>%
  ggplot(., aes(x = `Last Name`, y = `Percentage Completion`)) +
  geom_bar(stat = "identity", fill = "gray") +
  labs(
    x = "Student",
    y = "Percentage completion"
  ) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 100)) +
  coord_flip() +
  theme(legend.position = "none")

```

